---
title: ''
author: "Kalyan"
date: "11/19/2016"
output: html_document
---


### Housing Dataset Doubts
On comparing sentiment percentage with respect to different variable is see strange results boxplots.
Question : Is it okay to compare sentiment percentage with respect to differnt variables?.

```{r, echo=F}
housing = read.csv('HousingData.csv', sep=';')
housing$total = housing$Sentiment.Favorable + housing$Sentiment.Unfavorable
housing$pos_sent = housing$Sentiment.Favorable/housing$total
housing$neg_sent = housing$Sentiment.Unfavorable/housing$total
attach(housing)
ProximityClose = as.factor(ProximityClose)
ContactFrequent = as.factor(ContactFrequent)
NormaFavorable = as.factor(NormaFavorable)
str(housing)
par(mfrow=c(1,3))
boxplot(pos_sent ~ ProximityClose, ylab="Sentiment Positive", xlab = "Close Proximity")
boxplot(pos_sent ~ ContactFrequent, ylab="Sentiment Positive", xlab ="Contact Frequency")
boxplot(pos_sent ~ NormaFavorable, ylab="Sentiment Positive", xlab = "Norm Agree and Immigration Sentiment")
```

#### Interpretation for boxplot 1
Living close to immigrants generally does not have a huge effect on sentiment.
Question : Here personally I would assume that if I lived close the immigrants, I would have high of low sentiment.

#### Interpretation for boxplot 2
By being in contact with immigrant one tends to have a lower positive sentiment when compared to not being in contact.

#### Interpretation for boxplot 3
People who do not agree to norms generally tend to have a higher positive sentiment to immigration.
Question : I would assume the opposite. I am not sure if I am interpretting the data correctly.

#### Interpretting model

```{r}
m = cbind(Sentiment.Favorable,Sentiment.Unfavorable)
model = glm(m ~ ProximityClose+ContactFrequent+NormaFavorable, family = "binomial")
summary(model)
pchisq(2.2378, 8 - 3)
```

Question : How to use deviance and chisqure to decide if the model is good / Interpret the goodnes s of fit.
