---
title: "Grades"
author: "Krishna Kalyan"
date: "1/16/2017"
output: html_document
---

We were give grades data set and lets load it up in R. 

```{r}
rm(list=ls())
setwd('/Users/krishna/Downloads/exam/param')
load('Grades.Rdata')
Grades <- data.frame(Grades)
```

We begin by doing a summary on our dataset to understand the data better.

```{r}
dim(Grades)
summary(Grades)
```

We observe that our has $200$ observations and $2$ columns. We see that sat scores vary from $720$ to $1150$ and gpa varys from $0.790$ to $3.840$. We also observe that our data set are in different scales.

We would also like to see the distribution of our dataset.

```{r}
par(mfrow=c(1,2))
plot(Grades$gpa, col='red', pch=19)
plot(Grades$sat, col='blue', pch=19)
```

We observe that the dataset are randomly distributed. It would not make sense transforming it. 

1. Scatter plot and observation

```{r}
par(mfrow=c(1,1))
plot(Grades,col='blue', pch=19, main='Scatter plot GPA vs SAT')
```

We observe that our data has a linear positive trend. We can also observe that there are few extreme points. Knowing this like to know the correlation value and also create a box plots for my observations.


```{r}
par(mfrow=c(1,2))
model1 <- lm(gpa~sat, data=Grades)
summary(model1)
cor(Grades)
boxplot(Grades$gpa, main='GPA')
boxplot(Grades$sat, main='SAT')
```

We can say that our data is positively correlated $0.74$. I think this is in the higher side. Also with the box plots, I observe that GPA has more outlier values.

2. Model used with hyphothesis.
Based on the patterns observed in my data I see that there is a linear relationship between my response and predictors. I will use a `Linear Model` to analyse this data.
I will model my respone $GPA$ as a function of my predictor $SAT$. This can be also expressed as below.
$GPA ~ SAT$

```{r}
model_lm <- lm(gpa~sat, data=Grades)
summary(model_lm)
```

Based on the summary of the model, I conclude that it is not a very good model as I observe an $R^2$ of $0.56$ and see that $sat$ is a significant variable in my model with `p-value` less than $0.001$.

Ho : Our model fit the data well
H1 : Model does not represnt the data

We reject Ho as we see that the `p-value` is only $2.2e-16$ and see if we can improve this model.

3. Expected change in mean GPA when sat score inc by 50.
```{r}
gpa <- -1.192 + 0.003 * 50 
gpa
# I am not sure of this answer above

# Or it could be 50 multiplied by it coefficient
50 * 0.003
```

4. Coeffieceint of sat.

```{r}
model_lm$coefficients[2]
```

The value of sat is very small. Is it statistically different from zero. No because when its multiplied from grade it seems to have a positive value over all.

5. Interpretation of Residual standard error.

Residual standard error is exactly 0 then the model fits the data perfectly. $0.3994$ tells me that we dont have a very good model. 
Residual can be calculated from the formual below.
(y - yhat)

6. Intepret Multiple R square.

$0.5612$ is the value in the multiple R squared. Higher the value the better ($1$ is the best). We can say again here that we dont have a very good model. $R^2$ can be interpreted as the percentage of variance in the dependent variable that can be explained by the predictors.

7. Obtain confidence Intervals

```{r}
conf <- confint(model_lm,level = 0.95)
(conf)
```

8. Predicted Values

```{r}
values <- c(40, 152,196)
conf <- confint(model_lm,level = 0.95)
pred <- predict(model_lm, Grades)
pred[values]
```

We see that our predicted values are bad. Its always underestimating or giving us low values for sat.

9. Check model with plots. 
```{r}
par(mfrow=c(2,2))
plot(model_lm)
```

- Our residuals are normally distributed (QQ plot has a straight line)
- We observe not trend in the residual vs fitted plot. Hence we can our residuals are independnet.
- Homoscedasticity can be see in the residual vs leverage plot. We see a conic shape or any kind of shape which I think is bad from what I remember.

10. 
```{r}
anova(model_lm)
```
We can say that sat is a significant variable.

11. Large Residuals

```{r}
big_res <- which.max(model_lm$residuals) #this is the index
Grades[big_res,]
model_lm$residuals[big_res]
```

12. Analysis for conclusion

We dont have a very good model here. We can say that our model has not so good R^2 and there might be some unseen data that can better expain the response gpa.

13. Can the model be improved.

Yes the model can be improved by adding speaking to a domain expert and seeking for varible that can explain our model better. For example number of hours studied.